Effective Vaccination Strategies for an H1N1 Epidemic in Ithaca, New York

### 2015-10-01 final_submission/manuscript.tex
done SIR (mostly)

    The fraction of deaths remains small for all populations so it is not plotted. The total number of person-months of suffering is the integral of the green curve.
% \subsection{Analysis of Model (robustness)}
% 	//TODO
% \subsection{Strengths and Weaknesses}
% 	//TODO
% \subsection{Future Work}
% 	//TODO

>>>>

    The fraction of deaths remains small for all populations so it is not plotted. The total number of person-months of suffering is the integral of the green curve.

    Running this with vaccine distributions (.1, .4, .4, .1) results in the following MATLAB output:

    \begin{lstlisting}
        total_deaths =

            0.0030    0.2532    0.0529    0.0049

        total_suffering =

            1.0e+03 *

            0.0389    7.0540    3.0925    0.1686
    \end{lstlisting}

    Running this with vaccine distributions (.4, .1, .1, .4) results in the following MATLAB output:

    \begin{lstlisting}
        total_deaths =

            0.0020    0.2674    0.0579    0.0039

        total_suffering =

            1.0e+03 *

            0.0263    7.4504    3.3864    0.1356
    \end{lstlisting}
    Running this with vaccine distributions (.1, .4, .4, .1) and $\mu = \mu * 20$results in the following MATLAB output:

     \begin{lstlisting}
        total_deaths =

            0.0598    5.0633    1.0570    0.0979

        total_suffering =

            1.0e+03 *

            0.0389    7.0522    3.0919    0.1685
    \end{lstlisting}

    Running this with vaccine distributions (.4, .1, .1, .4) and $\mu = \mu * 20$results in the following MATLAB output:

    \begin{lstlisting}
        total_deaths =

            0.0403    5.3464    1.1572    0.0787

        total_suffering =

            1.0e+03 *

            0.0263    7.4485    3.3857    0.1356
    \end{lstlisting}
% \subsection{Analysis of Model (robustness)}
% 	//TODO
% \subsection{Strengths and Weaknesses}
% 	//TODO
% \subsection{Future Work}
% 	//TODO
